---
title: "ramenreview"
subtitle: "Exploring the ramen varieties around the world"
format:
  revealjs:
    incremental: true
    slide-number: true
    show-slide-number: print
    backgroundcolor: "#fee379"
editor: visual
author: "By Phuong Thanh Trinh"
---

## {background-color="#fee379"- background-image="https://upload.wikimedia.org/wikipedia/commons/f/fc/Kawaii_cat_eating_ramen.jpg"-background-size="1000px"}

```{r, echo = FALSE, message = FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(DT)
library(plotly)
library(kableExtra)
library(shiny)
```

```{r, message = FALSE, warning=FALSE}
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
```

## Aim of the package

::: incremental
-   Provides an overview about the diversity of ramen world

-   Understands the quality of different ramen brands as well as the popular packaging styles

-   Helps ramen enthusiasts to decide which ramen is worth to try and which brand they might want to avoid
:::

## Source

::: columns
::: {.column width="50%"}
The data used in this package is the `ramen_rating.csv` data set, originated from the [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/).
:::

::: {.column width="50%"}
Each record in the data set represents a single ramen review. The dataset contains the following 6 variables:

```{r}
tibble(
  "Variable" = c("brand", "variety", "style", "country", "review_number", 
                 "stars"),
  "Class" = c("character", "character", "character", "character", "numeric", 
              "numeric"),
  "Description" = c("Brand of the ramen",
                    "The ramen variety, e.g., a flavor, style, ingredient", 
                    "Style of container (cup, pack, tray)", 
                    "Origin country of the ramen brand",
                    "Ramen review number",
                    "Rating of the ramen ranging from 0-5 (5 is best, 0 is worst)")
) %>%
  kable() %>%
  kable_styling(full_width = F, font_size = 14,
                bootstrap_options = c("striped", "condensed", "bordered"))
```
:::
:::

## Demonstration of the package
### Functions

::: incremental
* `get_average`	Get the average ratings
* `get_best_style`	Get highest varieties
* `get_pct`	Get good and bad ramen from each country
* `get_ramen_rating`	Get ramen_rating dataset
* `get_rank`	Rank highest average rate
* `get_table`	Get ramen_rating dataset in tabular format
* `run_app`	Get shiny app for ramen rating dataset
:::


## Get the package 

::: {.incremental}

```{r, eval=TRUE, echo=TRUE}
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-PhuongThanhTrinh")
```

. . .

```{r, eval=TRUE, echo=TRUE}
# load the library
library(ramenreview)
```

:::

## `get_ramen_rating()` function 

The dataset has been slightly modified to fit with the purpose of this package, shown as the code below:

``` {r, eval=TRUE, echo=TRUE}

ramen_ratings <- ramen_ratings %>%
  drop_na(stars) %>%
  
  # recode countries' names
  mutate(country = ifelse(country == "Hong Kong", "China", country),
         country = ifelse(country == "Russia", "Russian Federation", country),
         country = ifelse(country == "Holland", "Netherlands", country),
         country = ifelse(country == "Dubai", "United Arab Emirates", country),
         country = ifelse(country == "South Korea", "Republic of Korea", country),
         country = ifelse(country == "Singapore", "Malaysia", country),
         country = ifelse(country == "Sarawak", "Malaysia", country),
         country = ifelse(country == "USA", "United States", country),
         country = ifelse(country == "UK", "United Kingdom", country),
         country = ifelse(country == "Phlippines", "Philippines", country))
```

## `get_ramen_rating()` function 

```{r, eval=TRUE, echo=TRUE}
#| eval: false
#| code-line-numbers: true
#| 
# assign countries to corresponding continents
asia <- c("Russia", "Thailand", "Japan", "Taiwan", "South Korea", "Hong Kong", "Malaysia", "China", "Philippines", "Vietnam", "Bangladesh", "Singapore", "Indonesia", "India", "Pakistan", "Nepal", "Myanmar", "Cambodia", "Dubai")
europe <- c("France", "Ukraine", "Netherlands", "Italy", "Poland", "Germany", "Hungary", "United Kingdom", "Finland", "Sweden", "Estonia")
oceania <- c("Australia", "New Zealand", "Fiji")
africa <- c("Nigeria", "Ghana")
america <- c("Canada", "United States", "Brazil", "Mexico", "Colombia")

  # create new variable named "continent"
ramen_ratings <- ramen_ratings %>%
  mutate(continent = case_when(
    country %in% asia ~ "Asia",
    country %in% europe ~ "Europe",
    country %in% oceania ~ "Oceania",
    country %in% america ~ "America",
    country %in% africa ~ "Africa")) 
```

## `get_ramen_rating()` function 

* This function will return a tibble including 3180 rows and 7 columns, as shown below:

``` {r}
get_ramen_rating()
```



# `get_table()` function { .smaller} 

* This function will return a tidy formatted table comprising 4 summary statistics for ramen from different countries.

{.scrollable}

```{r, echo=TRUE}
get_table()
```


## `get_pct()` function {.scrollable}

*Get the percentage of good and bad ramen in the data?*

* The histogram below shows the distribution of ramen brands being rated from a 5-score scale.

```{r echo=TRUE}
#| label: fig-ramen
#| fig-cap: "Distribution of ratings across brands"
ggplot(ramen_ratings, aes(x = stars)) +
  geom_histogram(color = "purple", fill = "purple", alpha = 0.2, bins = 20, aes(y = stat(density))) +
  geom_density(color = "purple", fill = "purple", alpha = 0.2) +
  labs(x = "Rating", y = "Number of ramen brands") 
```

The distribution of ratings is quite left-skewed.

-   Let's find out the rate among different countries with function `get_pct()`:

```{r, echo=TRUE}
get_pct(names = "Australia")
```


## `get_average` function

*Are you curious what is the average rate in which country? The below function can help answer this question:*

```{r, echo=TRUE}
get_average(continents = "Asia")
```

## `get_best_style` and `get_rank()` function

* To get the style with highest varieties
```{r, echo=TRUE}
get_best_style(styles = "Pack")
```

* To get the ranking of average rate for each ramen style

```{r, echo=TRUE}
get_rank(styles = "Bowl")
```

## `run_app()` function

* A Shiny app has been provided to help users gather information regarding different ramen reviews.

```{r, eval=FALSE}
run_app()
```


## {background-image="https://upload.wikimedia.org/wikipedia/commons/thumb/d/d6/Thank-new-yellow-transparent.svg/600px-Thank-new-yellow-transparent.svg.png?20200609150708"-background-size="1000px"}
