---
title: "Ramen World"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ramen World}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ramenreview)
```

# Overview

This is a Ramen Rating package.

The creator of this package is Phuong Thanh Trinh.

The data used for this assessment is the `ramen_rating.csv` data that is collected from the [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/).

The aim of this package is to provide users information regarding different ramen reviews and how different factors such as styles can change customers' ratings on a particular ramen brand.

# Dataset 

The data used for this assessment is the `ramen_rating.csv` data set, originated from the [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/) - a product review website for ramen enthusiast.

This dataset provides more than 3,000 reviews on over 400 ramen brands on selected countries across the globe. Each record in the data set represents a single ramen review. The dataset contains 6 variables, including:

4 categorical variables:

  - brand: Brand of the ramen

  - variety: The ramen variety, e.g., a flavor, style, ingredient

  - style: Style of container (cup, pack, tray)

  - country: Origin country of the ramen brand

2 numeric variables:

  - review_number: Ramen review number

  - stars: Rating of the ramen ranging from 0-5 (5 is best, 0 is worst)

# Inside

There are 7 functions included in this package:

* `get_average`	Get the average ratings
* `get_best_style`	Get highest varieties
* `get_pct`	Get good and bad ramen from each country
* `get_ramen_rating`	Get ramen_rating dataset
* `get_rank`	Rank highest average rate
* `get_table`	Get ramen_rating dataset in tabular format
* `run_app`	Get shiny app for ramen rating dataset


