---
title: "Ramen World"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Ramen World}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ramenreview)
```

# Overview

This is a Ramen Rating package.

The creator of this package is Phuong Thanh Trinh.

The data used for this assessment is the `ramen_rating.csv` data that is collected from the [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/).

The aim of this package is to provide users information regarding different ramen reviews and how different factors such as styles can change customers' ratings on a particular ramen brand.

# Dataset 

The data used for this assessment is the `ramen_rating.csv` data set, originated from the [Ramen Rater](https://www.theramenrater.com/resources-2/the-list/) - a product review website for ramen enthusiast.

This dataset provides more than 3,000 reviews on over 400 ramen brands on selected countries across the globe. Each record in the data set represents a single ramen review. The dataset contains 6 variables, including:

4 categorical variables:

  - brand: Brand of the ramen

  - variety: The ramen variety, e.g., a flavor, style, ingredient

  - style: Style of container (cup, pack, tray)

  - country: Origin country of the ramen brand

2 numeric variables:

  - review_number: Ramen review number

  - stars: Rating of the ramen ranging from 0-5 (5 is best, 0 is worst)

# Inside

There are three functions included in this package:

* `ramen_ratings()` function allows users to get the `ramen_rating.csv` data set. The dataset has been slightly modified to fit with the exploratory purpose of the package

* `five_sum()` function calculates the total number of ramen varieties available in each of the ramen brands

* `good_bad_ramen()` function generates a visialization showing the percentage of good and bad rated ramen based on countries


